Modular Deep Encoder-Decoders

### 2016-04-29 paper/draft.tex
Added Tools; Labor Division; Baseline Results;Hyperparameter tuning

In this short paper, we propose a Modular Deep Encoder-Decoder network (MDED) for text classification. The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data modality by adding a new encoder to the network. MDED has been applied to text classification on SaudiNewsNet. A modular Long Short Term Memory (LSTM) network is built. Experimental results show that our algorithm can efficiently combine new source of data and pre-trained model. (show some summaries of experimental results here)

@@

In this paper, we evaluate the effectiveness of idea by applying the concept towards a simple NLP classification task. We adopt an Arabic newspaper article database to classify into different journals based on the article content, author and title.

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.

@@

@@

%The procedure is quite straight-forward. While part of the team worked on
%building our tailored dataset, the other half worked on the model definition
%and training procedure.

@@

Training accuracy &  &  &  \\

Testing accuracy & & & \\

@@

%\end{multicols}
\end{document}

>>>>

In this short paper, we propose a Modular Deep Encoder-Decoder network (MDED) for text classification. The basic idea behind MDED is to extend a pre-trained model, which consists of a set of deep encoder-decoders, with an additional source of data modality by adding a new encoder to the network. MDED has been applied to text classification on Saudi Newspapers Arabic Corpus (SaudiNewsNet). A modular Long Short Term Memory (LSTM) network is built. Experimental results show that our algorithm can efficiently combine new source of data and pre-trained model. (show some summaries of experimental results here)

@@

In this paper, we evaluate the effectiveness of idea by applying the concept towards a simple NLP classification task. We adopt Saudi Newspapers Arabic Corpus \cite{hagrima2015} to classify text into different journals based on the article content, author and title.

\section{Method}\label{method}
\subsection{Materials}
\subsubsection{Corpora}
We use the freely available Saudi Newspapers Arabic Corpus \cite{hagrima2015}. The dataset contains a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.

@@

\subsubsection{Tools}
For training the neural networks, Neon toolkit was employed \cite{Neon}. Neon is Nervana's python based deep-learning library. The toolkit was chosen because of its flexibility of distributed training on both CPU and GPU and its good support for neural network components.

@@

\subsubsection{Hyper-parameter Tuning}
Using the development set, the hyper-parameters were fine-tuned for better performance. The tuning of sentence length cut-off for training the embedding layer was found to be critical especially when training on the content of articles. Setting lower sentence length resulted in over-training of the system. The distribution of the sentence lengths were plotted as shown in Figure~\ref{fig:sent_dist}. Looking at the distribution, we found the value of 2048 to be optimal. Different values for learning rate, hidden-layer dimensionality and non-linearity were experimented. 
%The procedure is quite straight-forward. While part of the team worked on
%building our tailored dataset, the other half worked on the model definition
%and training procedure.

@@

Training accuracy &  & 83.5207\% & 88.8635\% \\

Testing accuracy & & 79.7421 \% & 58.7276\% \\

@@

\newpage
\section{Labor Division}
\begin{itemize}
\item
  \textbf{Cheng:} \textbf{Coding} - Data retrieval, unzipping, reading, unicode decoding; \textbf{Report Writing} - Corpora, Evaluation.
\item
  \textbf{Quiangui:} Hyper-parameter tuning; \textbf{Report Writing} - Results, Abstract, Introduction.
\item
  \textbf{Prashanth:} \textbf{Coding} - Data pre-processing, Data partitioning,  Feature representation for embedding layer, Baseline system; \textbf{Report Writing} - Data pre-processing and features, Embedding Layer, Baseline System, Hyper-parameter tuning.
\item
  \textbf{Sebastian:} \textbf{Coding} - Neural Network training, Makefiles; \textbf{Report Writing} - Abstract, Introduction, Proposed System, Discussion.
\end{itemize}
\section{Word Count}
%\end{multicols}
\end{document}
